### 2024-06-24 analysis/analysis.qmd
added updated analysis
update get_study_results, add unique ids to analysis.Qmd

- Update 2024-06-19
- [ ] CA TODO: find better way to read in functions

@@

>>>>

- Update 2024-06-19
- [ ] CA TODO later (if at all): find better way to read in functions

@@

# add unique identifiers

unique_id <- apply(metaMER_results[,c('citekey',
                        'library_id',
                         'model_id',
                         'feature_id',
                         'data_id',
                         'experiment_id')],
                      1, 
                      paste0, 
                      collapse = '-'
) 
metaMER_results$unique_id <- stringr::str_remove_all(unique_id, 
                                                     ' ')

metaMER_results <- metaMER_results |> dplyr::select(unique_id, 
                                 dplyr::everything())
